IRS-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design

### 2020-10-29 main.tex
:art: Revise manuscript

	\begin{abstract}
		The performance of Simultaneous Wireless Information and Power Transfer (SWIPT) is mainly restricted by the strength of the received Radio-Frequency (RF) signal. To tackle this problem, we introduce a low-power Intelligent Reflecting Surface (IRS) that compensates the propagation loss and boosts the energy efficiency with a passive beamforming gain. This paper investigates an IRS-aided Orthogonal Frequency Division Multiplexing (OFDM) SWIPT system based on a practical nonlinear energy harvester model, where a multi-antenna Access Point (AP) transmits information and energy simultaneously to a single-antenna user under the assist of IRS. We aim to maximize the Rate-Energy (R-E) region through a joint optimization of the transmit waveform and active beamforming at the AP, the reflection coefficients at the IRS, and the power splitting ratio at the user. The performance of the proposed design is compared with those of no IRS, non-adaptive (information-optimized, power-optimized) IRS and ideal Frequency-Selective (FS) IRS, and we confirm that due to rectifier nonlinearity, a dedicated power signal can be beneficial to energy harvesting (EH). It has the consequence that the Time-Switching (TS) receiver is preferred over Power-Splitting (PS) receiver for multi-carrier transmission at a low Signal-to-Noise Ratio (SNR). Simulation results demonstrate that the proposed design based on a joint waveform, active and passive beamforming optimization brings effective R-E enhancement over benchmark schemes for broadband transmission. The adaptive passive beamforming design outperformed the benchmarks for broadband transmission, while the IRS only need to be optimized once for narrowband transmission.
	\end{abstract}

@@

			The concept of SWIPT was first cast in \cite{Varshney2008}, where the authors investigated the Rate-Energy (R-E) tradeoff for a flat Gaussian channel and typical discrete channels. Two co-localized information and power receivers were then proposed in \cite{Zhou2013}, namely Time Switching (TS) that switches between Energy Harvesting (EH) and Information Decoding (ID) modes, and Power Splitting (PS) that splits the received signal into individual components. Dedicated information and energy beamforming were then investigated in \cite{Zhang2013,Park2014} to characterize the R-E region for multi-antenna broadcast and interference channels.
			% Though SWIPT has been subsequently investigated in many scenarios \cite{Clerckx2019}, it was noticed more recently that the modeling of the energy harvester, and in particular its nonlinearity, has a crucial and significant impact on the signal preference, resource allocation and system design of WPT and any wireless-powered systems \cite{Trotter2009,Clerckx2016a,Clerckx2019}.
			% , and recommended waveforms with large Peak-to-Average Power Ratio (PAPR) to improve the power efficiency and system coverage
			On the other hand, \cite{Trotter2009} pointed out that the Radio Frequency-to-Direct Current (RF-to-DC) conversion efficiency depends on the rectifier input power level. It implies that the modeling of the energy harvester, in particular its nonlinearity, has a crucial and significant impact on the waveform preference, resource allocation and system design of any wireless-powered systems \cite{Trotter2009,Clerckx2018,Clerckx2019}. Motivated by this, \cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics, then implemented joint waveform and beamforming design for WPT. Simulation and experiments demonstrated the inaccuracy of the rectenna linear model and emphasized the benefit of modeling the rectifier nonlinearity in real system design \cite{Kim2019,Kim2020a}. Importantly, the joint waveform and beamforming strategy for WPT was also shown experimentally in \cite{Kim2020} to be a key technique to expand operation range. %Beyond WPT, the work in [10]
			The work was extended to SWIPT in \cite{Clerckx2018b}. Uniquely, it showed that the rectifier nonlinearity leads to radical changes to SWIPT design, namely 1) modulated and unmodulated waveforms are not equally suitable for wireless power delivery, 2) a multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform is useful to enlarge the R-E region of SWIPT, 3) a combination of power splitting and time sharing is in general the best strategy, 4) the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG), 5) the rectifier nonlinearity is beneficial to system performance and is essential to efficient SWIPT design. Those observations, validated experimentally in \cite{Kim2019},  led to the question "what is the optimal input distribution for SWIPT under nonlinearity?". This question was answered in \cite{Varasteh2020} for single-carrier SWIPT, and some attempts were further made in \cite{Varasteh2019d} for multi-carrier SWIPT. The answer sheds new light to fundamental limits of SWIPT and practical signaling (e.g. modulation and waveform) strategies. It is now well understood from \cite{Clerckx2018b,Varasteh2020,Varasteh2019d} that, due to the nonlinearity, a combination of CSCG and On-Off Keying in single-carrier setting and non-zero mean and asymmetric inputs in multi-carrier setting lead to significantly larger R-E region compared to conventional CSCG. Recently, \cite{Varasteh2020a} used machine learning techniques to design SWIPT signaling under nonlinearity to complement the information theoretic results of \cite{Varasteh2020} and new modulation schemes were subsequently designed.
		\end{subsection}

		\begin{subsection}{Intelligent Reflecting Surface}
			Intelligent Reflecting Surface (IRS) has recently emerged as a promising technique that adapts the wireless channel to increase spectrum and energy efficiency. In practice, an IRS consists of multiple individual reflecting elements that adjust the amplitude and phase of the incident signal through passive beamforming. Different from relay and backscatter, IRS assists the primary transmission using fully passive components, thus consumes less power with no additional thermal noise but is limited to frequency-flat (FF) reflection. Although Frequency-Selective Surface (FSS) has received much attention for wideband communications, it is different from IRS as active FSS requires RF-chains \cite{Kim2006} while passive FSS has fixed physical characteristics and is non-adaptive \cite{Anwar2018}.

			Inspired by the development of real-time reconfigurable metamaterials \cite{Cui2014}, the authors of \cite{Liaskos2018} introduced a programmable metasurface that steers or polarizes the EM wave at specific frequency to mitigate signal attenuation. Motivated by this, \cite{Wu2018} proposed an IRS-assisted Multiple-Input Single-Output (MISO) system and jointly optimized the precoder at the Access Point (AP) and the phase shifts at the IRS to minimize the transmit power. The active and passive beamforming problem was extended to the discrete phase shift case \cite{Wu2019a} and the multiuser case \cite{Wu2019}. Starting from the impedance equation, \cite{Abeywickrama2019} investigated the influence of phase shift on the reflection amplitude and proposed a parametric IRS model via curve fitting. In \cite{Nadeem2019}, channel estimation for Time-Division Duplex (TDD) systems was carried through a two-stage Minimum Mean Squared Error (MMSE)-based protocol that sequentially estimates the cascaded channel of each reflector with the others switched off. To reduce estimation overhead and design complexity, \cite{Yang2019} exploited the spatial correlation and proposed a group-based IRS model where adjacent elements share a common reflection coefficient. Recent research also explored the possibility of integrating IRS into Orthogonal Frequency-Division Multiplexing (OFDM) systems. For example, \cite{Yang2020} further enhances time diversity by dynamic passive beamforming that varies IRS over consequent time slots, which enables flexible resource allocation over time-frequency Resource Blocks (RBs). In \cite{Dai2020}, a prototype IRS with \num{256} \num{2}-bit elements based on Positive Intrinsic-Negative (PIN) diodes was developed to support real-time high-definition video transmission at \si{GHz} and mmWave frequency.
		\end{subsection}

		\begin{subsection}{IRS-aided SWIPT}
			The effective channel enhancement and low power consumption of IRS are expected to bring more opportunities to SWIPT. It was argued in \cite{Wu2020b} that dedicated energy beam is power-inefficient and may cause interference, thus not required to maximize the Weighted Sum-Power (WSP) for a multiuser IRS-assisted SWIPT system. On the other hand, \cite{Tang2019} suggested that if the interference can be cancelled, multiple energy beams are generally required for the max-min harvested power problem. \cite{Wu2020a} proposed a novel penalty-based algorithm, whose inner layer employs Block Coordinate Descent (BCD) method to update transmit precoders and IRS phase shifts while the outer layer updates the penalty coefficients. It demonstrated that Line-of-Sight (LoS) links can boost the harvested power because the rank-deficient channels are highly correlated. In such cases, a single energy stream is enough for all energy receivers.

@@

			\textit{Third}, we conduct numerical evaluations that demonstrate the benefit of the proposed architecture. It is confirmed that the observations for SWIPT carries on to IRS-aided SWIPT. For example, dedicated power waveform can boost the energy transmission efficiency for multi-carrier transmission, and TS and PS are preferred at low and high SNR, respectively. Results also confirmed that the IRS bring a significant channel amplification and R-E enhancement with no impact on the waveform preference and transceiving strategy. In contrast to the active amplify-and-forward relay whose optimal location is around the midpoint \cite{Li2017}, we observed that the passive IRS should be placed next to either the transmitter or the receiver to further improve the R-E tradeoff, due to the product-distance path loss model. It implies that that equipping the AP with an IRS can effectively extend the operation range of SWIPT systems. Also, the adaptive passive beamforming design slightly outperformed the fixed (information-optimized, power-optimized) design for broadband transmission, while the IRS only need to be optimized once for narrowband transmission.

@@

			Rectifiers consist of nonlinear components as diode and capacitor to produce DC output and store energy \cite{Pinuela2013}. Consider a simplified rectifier in Fig.~\ref{ci:single_diode_rectifier} where a single series diode is followed by a low-pass filter with a parallel load. Denote $i_s$ as the reverse bias saturation current, $n'$ as the diode ideality factor, $v_t$ as the thermal voltage, $v_d(t)=v_{\text{in}}(t)-v_{\text{out}}(t)$ as the voltage across the diode where $v_{\text{out}}(t)$ is the output voltage across the load. A Taylor expansion of the diode characteristic equation $i_d(t)=i_s(e^{v_d(t)/n' v_t}-1)$ around a quiescent operating point $a$ writes as $i_d(t)=\sum_{i=0}^{\infty}k_i'(v_d(t)-a)^i$, where $k_0'=i_s(e^{a/n' v_t}-1)$ and $k_i'=i_se^{a/n'v_t}/i!(n'v_t)^i$ for $i=1,\dots,\infty$. Note that this small-signal expansion model is only valid for the non-linear operation region, and the I-V relationship would be linear if the diode behavior is dominated by the load \cite{Clerckx2016a}. Also, an ideal low-pass filter with steady-state response can provide a constant $v_{\text{out}}$ that depends on the peak of $v_{\text{in}}(t)$ \cite{Curty2005}. Therefore, a proper choice of the operating voltage drop is $a=\mathcal{E}\{v_d(t)\}=-v_{\text{out}}$ such that
			\begin{equation}\label{eq:i_d}
				i_d(t)=\sum_{i=0}^{\infty}k_i'\rho^{i/2}R_{\text{ant}}^{i/2}y(t)^i\,.
			\end{equation}
			By discarding the non-DC components, taking expectation over symbol distribution, and truncating \ref{eq:i_d} to the $n_0$-th order, we approximate the average output DC current for a given channel as
			\begin{equation}\label{eq:i_out}
				i_{\text{out}}(t)=\mathcal{A}\{i_d(t)\}\approx\sum_{i=0}^{n_0}{k_i'}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}\mathcal{E}\left\{{\mathcal{A}\left\{y(t)^i\right\}}\right\}\,.
			\end{equation}
			With the assumption of evenly-spaced frequencies, it holds that $\mathcal{A}\left\{y(t)^i\right\}=0$ for odd $i$ thus the related terms have no contribution to DC output. However, $k_i'$ is still a function of $i_{\text{out}}$, and \cite{Clerckx2016a} proved that maximizing a truncated $i_{\text{out}}$ is equivalent to maximizing a monotonic function
			\begin{equation}\label{eq:z}
				z(\boldsymbol{\phi},\boldsymbol{w}_I,\boldsymbol{w}_P,\rho)=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{\mathcal{A}\left\{y(t)^i\right\}\right\}}
			\end{equation}
			where $k_i=i_s/i!(nv_t)^i$. It can be observed that the traditional linear harvester model, where the output DC power equals the sum of the power harvested on each frequency, is a special case of \ref{eq:z} with $n_0=2$. However, due to the coupling among different frequencies, some high-order AC components compensate each other and further contribute to the output DC power. In other words, even-order terms with $i \ge 4$ account for the nonlinear behavior of the diode. For simplicity, we let $\beta_2={k_2}{R_{\text{ant}}}$, $\beta_4={k_4}{R_{\text{ant}}^2}$ and choose $n_0=4$ to investigate fundamental rectifier nonlinearity. Note that $\mathcal{E}\left\{\lvert\tilde{x}_{I,n}\rvert^2\right\}=1$ but $\mathcal{E}\left\{\lvert\tilde{x}_{I,n}\rvert^4\right\}=2$, which can be interpreted as a modulation gain on the nonlinear terms of the output DC current. The corresponding $z$ is detailed in \ref{eq:z_expand}.

@@

			That is to say, for single-user MISO SWIPT, it is only necessary to determine the amplitudes $s_{I/P,n}$ at different tones. Hence, the original waveform optimization with $2MN$ complex variables is converted into a power allocation problem with $2N$ nonnegative real variables. Let $\boldsymbol{s}_{I/P}=[s_{I/P,1},\dots,s_{I/P,N}]^T \in \mathbb{C}^{N \times 1}$. At subband $n$, the effective channel gain is given by $\lVert{\boldsymbol{h}_n}\rVert$, and the power allocated to the modulated and unmodulated waveform are given by $s_{I,n}^2$ and $s_{P,n}^2$, respectively. With such an active beamformer selection, we have $\boldsymbol{h}_n^H\boldsymbol{w}_{I,n}=\lvert{\boldsymbol{h}_n^H\boldsymbol{w}_{I,n}}\rvert=\lVert{\boldsymbol{h}_n}\rVert s_{I,n}$ such that the rate and objective function further reduces to \ref{eq:R_waveform} and \ref{eq:z_waveform}, respectively.

@@

			where $m_P=(2N^3+6N^2+7N)/3$, $m_{I,n}=2$ are the number of monomials in the corresponding posynomials. Following \cite{Chiang2005}, we upper bound posynomials \ref{eq:posynomial_objective} and \ref{eq:posynomial_rate} by Arithmetic Mean-Geometric Mean (AM-GM) inequality such that problem~\ref{op:waveform_rgp} reduces to

@@

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=\linewidth}
				\input{assets/scaling_tx.tex}
			\end{adjustbox}
			\caption{Average WIT SNR and WPT DC current versus $M$ for $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$, $d_H=0$ and $d_V=0.5\,\si{\meter}$.}
			\label{fi:scaling_tx}
		\end{figure}

@@

		The number of transmit antennas $M$ and IRS reflectors $L$ influence the average R-E tradeoff as revealed in \ref{fi:re_tx} and Fig.~\ref{fi:re_reflector}. \textit{First,} it is observed that adding either active or passive elements benefits both information and power transmission while preserving the concavity-convexity of the R-E region. This is because increasing $M$ or $L$ indeed enhances the equivalent composite channel strength such that the magnitude of the terms in \ref{eq:z_expand} is amplified while the number remains unchanged. Therefore, it is concluded that the number of active and passive elements have no impact on the waveform preference and transceiving strategy. \textit{Second,} the R-E benefit of passive beamforming scales faster than that of active beamforming. This behavior is more obvious in Fig.~\ref{fi:scaling_tx} and \ref{fi:scaling_reflector} that illustrate the performance of WIT and WPT versus $M$ and $L$. For the active MRT beamforming, doubling $M$ brings a \SI{3}{\dB} gain at the average output SNR, corresponding to a transmit array gain of $M$ and a doubled harvester input power. Due to the rectifier nonlinearity, the output DC power ends up with a nearly four-time increase, and the design based on nonlinear model notably outperforms the linear one. On the other hand, when the IRS is very closed to the transmitter or the receiver, doubling $L$ can bring an array gain up to \SI{6}{\dB}. An interpretation is that the IRS collects $L$ signal copies with a receive array gain $L$, then performs an equal gain reflection with a reflect array gain $L$, achieving a total array gain of $L^2$. As a consequence, doubling $L$ brings a [TODO]-fold boost on the received signal power that further amplifies the harvested DC power by [TODO] times. However, the diode nonlinear model is based on a small-signal expansion and the input-output relationship would be linear in the high-power regime. These results emphasize the effectiveness of passive beamforming and the importance of modelling rectifier nonlinearity in the system design. \textit{Third,} using only few transmit antenna can achieve the performance of numerous reflectors with a much lower complexity. The reason is that the system performance in our setup is dominated by the AP-user direct link with the optimal active beamformer obtained in closed form. As shown in Fig.~\ref{fi:path_loss}, the direct path loss $\Lambda_D$ is in the scope of \num{e-7} while the extra path loss product $\Lambda_I\Lambda_R$ is below \num{e-10}. Therefore, although increasing $L$ can significantly enhance the AP-IRS-user extra channel, its amplitude is still too small compared with the direct channel such that increasing $M$ can be more efficient for a practical configuration. Another explanation is that the RF-chains of active antennas provide design flexibility in the frequency domain while the frequency-flat characteristic of IRS restricts its benefit for broadband transmission. On the contrary, a large number of active antennas suffer from channel hardening while the IRS can use adaptive reflection to potentially mitigate the effect. As a consequence, active beamforming is more effective for small-scale SWIPT where the direct channel dominates the transmission, and passive beamforming can be more effective for large-scale SWIPT where the extra channel dominates the transmission.

>>>>

	\begin{abstract}
		The performance of Simultaneous Wireless Information and Power Transfer (SWIPT) is mainly restricted by the strength of the received Radio-Frequency (RF) signal. To tackle this problem, we introduce a low-power Intelligent Reflecting Surface (IRS) that compensates propagation loss and boosts energy efficiency by adaptive passive beamforming. This paper investigates an IRS-aided Orthogonal Frequency Division Multiplexing (OFDM) SWIPT system based on a practical nonlinear energy harvester model, where a multi-antenna Access Point (AP) transmits information and power simultaneously to a single-antenna user under the assist of an IRS. Considering rectifier nonlinearity, we aim to maximize the Rate-Energy (R-E) region through a joint optimization of the transmit waveform and active beamforming at the AP, the reflection coefficients at the IRS, and the power splitting ratio at the user. Stationary solutions are achieved based on Alternating Optimization (AO) technique, where the optimal active beamforming is obtained in closed form, the passive beamforming is optimized by Successive Convex Approximation (SCA) technique, and the waveform and splitting ratio are optimized by Geometric Programming (GP) technique. It is confirmed that due to rectifier nonlinearity, a dedicated power signal can be beneficial to energy harvesting (EH), such that the Time-Switching (TS) receiver is preferred over Power-Splitting (PS) receiver for multi-carrier transmission at a low Signal-to-Noise Ratio (SNR). Simulation results also show that the introduction of IRS significantly enlarges the R-E region while preserving the waveform preference and transceiving strategy. Although the AP-IRS-user extra link is relatively weak, we found that the information and power benefits of passive beamforming scale much faster than those of active beamforming. It suggests using more active antennas for small-scale SWIPT and more passive elements for large-scale SWIPT.
	\end{abstract}

@@

			The concept of SWIPT was first cast in \cite{Varshney2008}, where the authors investigated the Rate-Energy (R-E) tradeoff for a flat Gaussian channel and typical discrete channels. Two co-localized information and power receivers were then proposed in \cite{Zhou2013}, namely Time Switching (TS) that switches between Energy Harvesting (EH) and Information Decoding (ID) modes, and Power Splitting (PS) that splits the received signal into individual components. Dedicated information and energy beamforming were then investigated in \cite{Zhang2013,Park2014} to characterize the R-E region for multi-antenna broadcast and interference channels. On the other hand, \cite{Trotter2009} pointed out that the RF-to-Direct Current (DC) conversion efficiency depends on the rectifier input power level. It implies that the modeling of the energy harvester, in particular its nonlinearity, has a crucial and significant impact on the waveform preference, resource allocation and system design of any wireless-powered systems \cite{Trotter2009,Clerckx2018,Clerckx2019}. Motivated by this, \cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics, then implemented joint waveform and beamforming design for WPT. Simulation and experiments demonstrated the inaccuracy of the rectenna linear model and emphasized the benefit of modeling the rectifier nonlinearity in real system design \cite{Kim2019,Kim2020a}. Importantly, the joint waveform and beamforming strategy for WPT was also shown experimentally in \cite{Kim2020} to be a key technique to expand operation range. Beyond WPT, the work in \cite{Clerckx2016a} was extended to SWIPT in \cite{Clerckx2018b}. Uniquely, it showed that the rectifier nonlinearity leads to radical changes to SWIPT design, namely 1) modulated and unmodulated waveforms are not equally suitable for wireless power delivery, 2) a multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform is useful to enlarge the R-E region of SWIPT, 3) a combination of power splitting and time sharing is in general the best strategy, 4) the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG), 5) the rectifier nonlinearity is beneficial to system performance and is essential to efficient SWIPT design. Those observations, validated experimentally in \cite{Kim2019},  led to the question "what is the optimal input distribution for SWIPT under nonlinearity?". This question was answered in \cite{Varasteh2020} for single-carrier SWIPT, and some attempts were further made in \cite{Varasteh2019d} for multi-carrier SWIPT. The answer sheds new light to fundamental limits of SWIPT and practical signaling (e.g. modulation and waveform) strategies. It is now well understood from \cite{Clerckx2018b,Varasteh2020,Varasteh2019d} that, due to the nonlinearity, a combination of CSCG and On-Off Keying in single-carrier setting and non-zero mean and asymmetric inputs in multi-carrier setting lead to significantly larger R-E region compared to conventional CSCG. Recently, \cite{Varasteh2020a} used machine learning techniques to design SWIPT signaling under nonlinearity to complement the information theoretic results of \cite{Varasteh2020} and new modulation schemes were subsequently designed.
		\end{subsection}

		\begin{subsection}{Intelligent Reflecting Surface}
			Intelligent Reflecting Surface (IRS) has recently emerged as a promising technique that adapts the wireless channel to increase spectrum and energy efficiency. In practice, an IRS consists of multiple individual reflecting elements that adjust the amplitude and phase of the incident signal through passive beamforming. Different from relay and backscatter, IRS assists the primary transmission using fully passive components, thus consumes less power with no additional thermal noise but is limited to Frequency-Flat (FF) reflection. Although Frequency-Selective Surface (FSS) has received much attention for wideband communications, it is different from IRS as active FSS requires RF-chains \cite{Kim2006} while passive FSS has fixed physical characteristics and is non-adaptive \cite{Anwar2018}.

			Inspired by the development of real-time reconfigurable metamaterials \cite{Cui2014}, the authors of \cite{Liaskos2018} introduced a programmable metasurface that steers or polarizes the EM wave at specific frequency to mitigate signal attenuation. Motivated by this, \cite{Wu2018} proposed an IRS-assisted Multiple-Input Single-Output (MISO) system and jointly optimized the precoder at the Access Point (AP) and the phase shifts at the IRS to minimize the transmit power. The active and passive beamforming problem was extended to the discrete phase shift case \cite{Wu2019a} and the multiuser case \cite{Wu2019}. Starting from the impedance equation, \cite{Abeywickrama2019} investigated the influence of phase shift on the reflection amplitude and proposed a parametric IRS model via curve fitting. In \cite{Nadeem2019}, channel estimation for Time-Division Duplex (TDD) systems was carried through a two-stage Minimum Mean Squared Error (MMSE)-based protocol that sequentially estimates the cascaded channel of each reflector with the others switched off. To reduce estimation overhead and design complexity, \cite{Yang2019} exploited the spatial correlation and proposed a group-based IRS model where adjacent elements share a common reflection coefficient. Recent research also explored the possibility of integrating IRS into Orthogonal Frequency-Division Multiplexing (OFDM) systems. For example, \cite{Yang2020} further enhances time diversity by dynamic passive beamforming that varies IRS over consequent time slots, to enable flexible resource allocation over time-frequency Resource Blocks (RBs). In \cite{Dai2020}, a prototype IRS with \num{256} \num{2}-bit elements based on Positive Intrinsic-Negative (PIN) diodes was developed to support real-time high-definition video transmission at \si{GHz} and mmWave frequency.
		\end{subsection}

		\begin{subsection}{IRS-Aided SWIPT}
			The effective channel enhancement and low power consumption of IRS are expected to bring more opportunities to SWIPT. It was argued in \cite{Wu2020b} that dedicated energy beam is power-inefficient and may cause interference, thus not required to maximize the Weighted Sum-Power (WSP) for a multiuser IRS-assisted SWIPT system. On the other hand, \cite{Tang2019} suggested that if the interference can be cancelled, multiple energy beams are generally required for the max-min harvested power problem. \cite{Wu2020a} proposed a novel penalty-based algorithm, whose inner layer employs Block Coordinate Descent (BCD) method to update transmit precoders and IRS phase shifts while the outer layer updates the penalty coefficients. It demonstrated that Line-of-Sight (LoS) links can boost the harvested power because the rank-deficient channels are highly correlated. In such cases, a single energy stream is enough for all energy receivers.

@@

			\textit{Third}, we conduct numerical evaluations that demonstrate the benefit of the proposed architecture. It is confirmed that the observations for SWIPT carries on to IRS-aided SWIPT. For example, dedicated power waveform can boost the energy transmission efficiency for multi-carrier transmission, while TS and PS are preferred at low and high SNR, respectively. Results also confirmed that the IRS bring a significant channel amplification and R-E enhancement with no impact on the waveform preference and transceiving strategy. Different from the active amplify-and-forward relay with optimal location around the midpoint \cite{Li2017}, the passive IRS should be placed next to either the transmitter or the receiver, due to the product-distance path loss model. It implies that that equipping the AP with an IRS can effectively extend the operation range of SWIPT systems. For active beamforming, increasing the number of transmit antennas brings a linear growth in SNR and a quadratic boost in harvested DC power. For passive beamforming, increasing the number of reflect elements provides a quadratic growth in SNR and a quartic boost in harvested DC power. Moreover, the adaptive IRS design outperforms the non-adaptive (rate/energy-optimized) ones for broadband transmission, while the performance of all three strategies coincides with the ideal Frequency-Selective (FS) IRS for narrowband transmission.

@@

			Rectifiers consist of nonlinear components as diode and capacitor to produce DC output and store energy \cite{Pinuela2013}. Consider a simplified rectifier model in Fig.~\ref{ci:single_diode_rectifier} where a single series diode is followed by a low-pass filter with a parallel load. Denote $i_s$ as the reverse bias saturation current, $n'$ as the diode ideality factor, $v_t$ as the thermal voltage, $v_d(t)=v_{\text{in}}(t)-v_{\text{out}}(t)$ as the voltage across the diode where $v_{\text{out}}(t)$ is the output voltage across the load. A Taylor expansion of the diode characteristic equation $i_d(t)=i_s(e^{v_d(t)/n' v_t}-1)$ around a quiescent operating point $a$ writes as $i_d(t)=\sum_{i=0}^{\infty}k_i'(v_d(t)-a)^i$, where $k_0'=i_s(e^{a/n' v_t}-1)$ and $k_i'=i_se^{a/n'v_t}/i!(n'v_t)^i$ for $i=1,\dots,\infty$. Note that this small-signal expansion model is only valid for the non-linear operation region, and the I-V relationship would be linear if the diode behavior is dominated by the load \cite{Clerckx2016a}. Also, an ideal low-pass filter with steady-state response can provide a constant $v_{\text{out}}$ that depends on the peak of $v_{\text{in}}(t)$ \cite{Curty2005}. Therefore, a proper choice of the operating voltage drop is $a=\mathcal{E}\{v_d(t)\}=-v_{\text{out}}$ such that
			\begin{equation}\label{eq:i_d}
				i_d(t)=\sum_{i=0}^{\infty}k_i'\rho^{i/2}R_{\text{ant}}^{i/2}y(t)^i\,.
			\end{equation}
			By discarding the non-DC components, taking expectation over symbol distribution, and truncating \ref{eq:i_d} to the $n_0$-th order, we approximate the average output DC current for a given channel as
			\begin{equation}\label{eq:i_out}
				i_{\text{out}}(t)=\mathcal{A}\{i_d(t)\}\approx\sum_{i=0}^{n_0}{k_i'}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}\mathcal{E}\left\{{\mathcal{A}\left\{y(t)^i\right\}}\right\}\,.
			\end{equation}
			With the assumption of evenly-spaced frequencies, it holds that $\mathcal{A}\left\{y(t)^i\right\}=0$ for odd $i$ thus the related terms have no contribution to DC output. However, $k_i'$ is still a function of $i_{\text{out}}$, and \cite{Clerckx2016a} proved that maximizing a truncated $i_{\text{out}}$ is equivalent to maximizing a monotonic function
			\begin{equation}\label{eq:z}
				z(\boldsymbol{\phi},\boldsymbol{w}_I,\boldsymbol{w}_P,\rho)=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{\mathcal{A}\left\{y(t)^i\right\}\right\}}
			\end{equation}
			where $k_i=i_s/i!(nv_t)^i$. It can be observed that the traditional linear harvester model, where the output DC power equals the sum of the power harvested on each frequency, is a special case of \ref{eq:z} with $n_0=2$. However, due to the coupling among different frequencies, some high-order AC components compensate each other and further contribute to the output DC power. In other words, even-order terms with $i \ge 4$ account for the nonlinear behavior of the diode. For simplicity, we let $\beta_2={k_2}{R_{\text{ant}}}$, $\beta_4={k_4}{R_{\text{ant}}^2}$ and choose $n_0=4$ to investigate fundamental rectifier nonlinearity. Note that $\mathcal{E}\left\{\lvert\tilde{x}_{I,n}\rvert^2\right\}=1$ but $\mathcal{E}\left\{\lvert\tilde{x}_{I,n}\rvert^4\right\}=2$, which can be interpreted as a modulation gain on the nonlinear terms of the output DC current. The corresponding $z$ is detailed in \ref{eq:z_expand}.

@@

			That is to say, for single-user MISO SWIPT, the optimal active beamformer is MRT and we only need to determine the amplitudes $s_{I/P,n}$ at different tones. Hence, the original waveform optimization with $2MN$ complex variables is converted into a power allocation problem with $2N$ nonnegative real variables. Let $\boldsymbol{s}_{I/P}=[s_{I/P,1},\dots,s_{I/P,N}]^T \in \mathbb{C}^{N \times 1}$. At subband $n$, the effective channel gain is given by $\lVert{\boldsymbol{h}_n}\rVert$, and the power allocated to the modulated and unmodulated waveform are given by $s_{I,n}^2$ and $s_{P,n}^2$, respectively. With such an active beamformer selection, we have $\boldsymbol{h}_n^H\boldsymbol{w}_{I,n}=\lvert{\boldsymbol{h}_n^H\boldsymbol{w}_{I,n}}\rvert=\lVert{\boldsymbol{h}_n}\rVert s_{I,n}$ such that the rate and objective function further reduces to \ref{eq:R_waveform} and \ref{eq:z_waveform}, respectively.

@@

			where $m_P=(2N^3+6N^2+7N)/3$, $m_{I,n}=2$ are the number of monomials. Following \cite{Chiang2005}, we upper bound posynomials \ref{eq:posynomial_objective} and \ref{eq:posynomial_rate} by Arithmetic Mean-Geometric Mean (AM-GM) inequality such that problem~\ref{op:waveform_rgp} reduces to

@@

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=\linewidth}
				\input{assets/scaling_tx.tex}
			\end{adjustbox}
			\caption{Average WIT SNR and WPT DC current versus $M$ for $L=20$, $N=16$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$, $d_H=0$ and $d_V=0.5\,\si{\meter}$.}
			\label{fi:scaling_tx}
		\end{figure}

@@

		The number of transmit antennas $M$ and IRS reflectors $L$ influence the average R-E tradeoff as revealed in \ref{fi:re_tx} and Fig.~\ref{fi:re_reflector}. \textit{First,} it is observed that adding either active or passive elements benefits both information and power transmission while preserving the concavity-convexity of the R-E region. This is because increasing $M$ or $L$ indeed enhances the equivalent composite channel strength such that only the magnitude of the terms in \ref{eq:z_expand} is amplified. Therefore, it is concluded that the number of active and passive elements have no impact on the waveform preference and transceiving strategy. \textit{Second,} the R-E benefit of passive beamforming scales faster than that of active beamforming. This behavior is more obvious in Fig.~\ref{fi:scaling_tx} and \ref{fi:scaling_reflector} that illustrate the performance of WIT and WPT versus $M$ and $L$. For the active MRT beamforming, doubling $M$ brings a \SI{3}{\dB} gain at the average output SNR, corresponding to a transmit array gain of $M$ and a doubled harvester input power. Due to the rectifier nonlinearity, the output DC current ends up with a nearly four-time (\SI{12}{\dB}) increase, validating the active scaling law in the order of $M^2$ \cite{Clerckx2016a}. On the other hand, when the IRS is very closed to the transmitter or the receiver, doubling $L$ can bring a SNR boost up to \SI{6}{\dB}, corresponding to an reflect array gain of $L^2$. An interpretation is that the IRS collects $L$ signal copies with a receive array gain $L$, then performs an equal gain reflection with a transmit array gain $L$, achieving a total gain of $L^2$. As a consequence, doubling $L$ brings a four-fold boost on the received signal power that further amplifies the harvested DC current by 16 times (\SI{24}{\dB}), suggesting a passive scaling law in the order of $L^4$. Besides, by considering harvester nonlinearity, the proposed design brings a \SI{20}{\dB} increase in the output DC current over conventional linear perspective. However, the diode nonlinear model is based on a small-signal expansion and the input-output relationship would be linear in the high-power regime. These results emphasize the effectiveness of passive beamforming and the importance of modelling rectifier nonlinearity in the system design. \textit{Third,} using only few transmit antenna can achieve the performance of numerous reflectors in a much lower complexity. The reason is that the system performance in our setup is dominated by the AP-user direct link, with the optimal active beamformer obtained in closed form. As shown in Fig.~\ref{fi:path_loss}, the direct path loss $\Lambda_D$ is in the scope of \num{e-7} while the extra path loss product $\Lambda_I\Lambda_R$ is below \num{e-10}. Therefore, although increasing $L$ can significantly enhance the AP-IRS-user extra channel, its amplitude is still too small compared with the direct channel such that increasing $M$ can be more efficient for a practical configuration. Another explanation is that the RF-chains of active antennas provide design flexibility in the frequency domain while the frequency-flat characteristic of IRS restricts its benefit for broadband transmission. On the contrary, a large number of active antennas suffer from channel hardening while the IRS can use adaptive reflection to potentially mitigate the effect. As a consequence, active beamforming is more effective for small-scale SWIPT where the direct channel dominates the transmission, and passive beamforming can be more effective for large-scale SWIPT where the extra channel dominates the transmission.
